\documentclass{article}
\usepackage{amsmath}
\usepackage{geometry}
\begin{document}

\section*{Problem 1}
\textbf{Problem:}
In the diagram below, we have $\sin \angle RPQ = \frac{7}{25}$.  What is $\sin \angle RPS$?

[asy]
pair R,P,Q,SS;
SS = (-2,0);
P = (0,0);
Q = (2,0);
R = rotate(aSin(7/25))*(1.5,0);
dot("$S$",SS,S);
do...

\textbf{Ground Truth:} \frac{7

\textbf{Baseline Answer:} \frac{25

\textbf{Finetuned Answer:} \frac{7

\newpage

\section*{Problem 2}
\textbf{Problem:}
Cylinder $B$'s height is equal to the radius of cylinder $A$ and cylinder $B$'s radius is equal to the height $h$ of cylinder $A$. If the volume of cylinder $A$ is twice the volume of cylinder $B$, th...

\textbf{Ground Truth:} 4

\textbf{Baseline Answer:} 2

\textbf{Finetuned Answer:} 4

\newpage

\section*{Problem 3}
\textbf{Problem:}
Either increasing the radius or the height of a cylinder by six inches will result in the same volume. The original height of the cylinder is two inches. What is the original radius in inches?

\textbf{Ground Truth:} 6

\textbf{Baseline Answer:} None

\textbf{Finetuned Answer:} 6

\newpage

\section*{Problem 4}
\textbf{Problem:}
In triangle $ABC$, we have that $E$ and $F$ are midpoints of sides $\overline{AC}$ and $\overline{AB}$, respectively. The area of $\triangle ABC$ is 24 square units. How many square units are in the a...

\textbf{Ground Truth:} 6

\textbf{Baseline Answer:} 3

\textbf{Finetuned Answer:} 6

\newpage

\section*{Problem 5}
\textbf{Problem:}
The diagonals of a regular hexagon have two possible lengths. What is the ratio of the shorter length to the longer length? Express your answer as a common fraction in simplest radical form.

\textbf{Ground Truth:} \frac{\sqrt{3

\textbf{Baseline Answer:} \frac{1

\textbf{Finetuned Answer:} \frac{\sqrt{3

\newpage

\section*{Problem 6}
\textbf{Problem:}
A solid box is 15 cm by 10 cm by 8 cm. A new solid is formed by removing a cube 3 cm on a side from each corner of this box. What percent of the original volume is removed?

\textbf{Ground Truth:} 18\%

\textbf{Baseline Answer:} 18

\textbf{Finetuned Answer:} 18\%

\newpage

\section*{Problem 7}
\textbf{Problem:}
Three congruent isosceles triangles $DAO$, $AOB$ and $OBC$ have $AD=AO=OB=BC=10$ and $AB=DO=OC=12$.  These triangles are arranged to form trapezoid $ABCD$, as shown.  Point $P$ is on side $AB$ so that...

\textbf{Ground Truth:} 12

\textbf{Baseline Answer:} 4

\textbf{Finetuned Answer:} 12

\newpage

\end{document}
